Relative parabolic factorizations of Chevalley groups

### 2015-09-06 dennis-vaserstein.tex
t_\alpha -> x_\alpha

Specializing identity~\eqref{rel:CCF} to the odd orthogonal (resp. symplectic) case we get:
\begin{equation} \label{rel:CCF-specBC} t_{1,0}(ab) = [t_{1, 2}(a), t_{2, 0}(b)] \cdot t_{1,-2}(-a b^2), \quad t_{1,-1}(-ab^2) = t_{-2,1}(ab) \cdot [t_{-2, 2}(a), t_{2, -1}(b)]. \end{equation}
Clearly, the root subgroup $X_{2, 0}(R)$ (resp. $X_{-2,2}(R)$) is contained in $\E(\Delta_s, R) \subseteq N_{rs}$ while we already know by the above argument that the subgroups $X_{2, 0}(R)$, $X_{1,-2}(R)$
(resp. $X_{-2,1}(R)$, $X_{2,-1}(R)$) are contained in $N_{rs}$.

@@

Just as in the above argument all the cases except $\Phi = \rB_\ell, \rC_\ell$ follow from~\cref{item-trans2}.
The proof in the case $\Phi=\rB_\ell$ is also similar to the one presented above.
Indeed, from the identity $t_{0, 1}(-a) = [t_{2,1}(-a); t_{0, 2}(-1)] t_{-2,1}(a)$ we conclude that
$$X_{0,1}(I) \subseteq X_{2,1}(I) \cdot X_{2,1}(I)^{t_{0,2}(1)} \cdot X_{-2,1}(I) \subseteq L_{rs} \cdot L_{rs}^{N_{rs}} \cdot L_{rs} \subseteq L_{rs}.$$

>>>>

Specializing identity~\eqref{rel:CCF} to the odd orthogonal (resp. symplectic) case we get:
\begin{align*} \label{rel:CCF-specBC}
& x_{1,0}(ab) = [x_{1, 2}(a), x_{2, 0}(b)] \cdot x_{1,-2}(-a b^2), \\
& x_{1,-1}(-ab^2) = x_{-2,1}(ab) \cdot [x_{-2, 2}(a), x_{2, -1}(b)].
\end{align*}
Clearly, the root subgroup $X_{2, 0}(R)$ (resp. $X_{-2,2}(R)$) is contained in $\E(\Delta_s, R) \subseteq N_{rs}$ while we already know by the above argument that the subgroups $X_{2, 0}(R)$, $X_{1,-2}(R)$
(resp. $X_{-2,1}(R)$, $X_{2,-1}(R)$) are contained in $N_{rs}$.

@@

Just as in the above argument all the cases except $\Phi = \rB_\ell, \rC_\ell$ follow from~\cref{item-trans2}.
The proof in the case $\Phi=\rB_\ell$ is also similar to the one presented above.
Indeed, from the identity $x_{0, 1}(-a) = [x_{2,1}(-a), x_{0, 2}(-1)]\cdot x_{-2,1}(a)$ we conclude that
$$X_{0,1}(I) \subseteq X_{2,1}(I) \cdot X_{2,1}(I)^{t_{0,2}(1)} \cdot X_{-2,1}(I) \subseteq L_{rs} \cdot L_{rs}^{N_{rs}} \cdot L_{rs} \subseteq L_{rs}.$$
